---
title: "EEB603_Github_Tutorial"
author: "KateMarkham"
date: "September 6, 2018"
output: html_document
---
setwd("H:/Coursework/EEB603/EEB603Tutorial")
#testtest
# Online

First register for a github account at www.github.com

# Load necessary R packages
```{r}
install.packages("installr")
install.packages("knitr")
library(installr)
library("knitr", lib.loc="~/R/win-library/3.4")
```

#Make sure your version of R is updated and current

```{r}
updateR()
```

#Web resources that are great

http://happygitwithr.com/ 


#Glossary
Branch-Parallel version of a repository. Working on a branch allows you to work without changing the live version on the master branch.
Clone-Copy of a reposity that is on your machine rather than on the server. (Can also act as a verb.) You can sync changes in your cloned copy to remote versions when you are online.
Commit-Changes to a file. It's similar to a "save as"" but you do not need to rename the file (Git automatically keeps track of each change). 
Fetch-Grabbing the latest version from an online repository-does not automatically merge this version with your own. 